Computing in the Field of Rationals

### 2012-06-26 rational_ext.tex
_

We present the categorical structure with minimum commentary. More
details may be found in excellent references such as Barr and Wells
[CITE] and Selinger \cite{springerlink:10.1007/978-3-642-12821-94}.

@@

>>>>

We present the categorical structure with minimum commentary. More
details may be found in excellent references such as Barr and Wells
[CITE] and Selinger \cite{springerlink:10.1007/978-3-642-12821-94}.
For brevity, we don't re-state standard categorical definitions and
subsequently present their {{Pi}} equivalents. Instead, we directly
state categorical definitions in terms of {{Pi}} types and
combinators, and provide appropriate references to the former. For
example, associativity is denoted by the greek letter $\alpha$ (and
$\alpha^{-1}$) in standard definitions, whereas we use {{assocl*}}
(and {{assocr*}}).

@@

\roshan{Should we show completeness -- i.e. that every relation is
  expressible? We can. But should we?}
